\huge Tor's Usability for Censorship Circumvention

### 2016-05-08 pets2017-paper/pets2017-paper.tex
Fix percentage of time on each screen.
David found a bug that did not pad edges to maxtime.

@@

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	All & 7\% & 5\% & 4\% & 58\% \\
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 6\% & 5\% & 5\% & 80\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 4\% & 3\% & 5\% & 78\% \\
	E3-OLD & 3\% & 11\% & 6\% & 60\% \\
	% (median, total) 
	%All & (7, 5)\% & (5, 17)\% & (4, 6)\% & (58, 64)\% \\
	%E1-NEW & (28, 34)\% & (0, 4)\% & (0, 6)\% & (60, 50)\% \\
	%E1-OLD & (30, 23)\% & (0, 35)\% & (0, 9)\% & (29, 21)\% \\
	%E2-NEW & (6, 5)\% & (5, 4)\% & (5, 4)\% & (80, 80)\% \\
	%E2-OLD & (7, 4)\% & (18, 22)\% & (8, 4)\% & (45, 66)\% \\
	%E3-NEW & (4, 6)\% & (3, 7)\% & (5, 4)\% & (78, 70)\% \\
	%E3-OLD & (3, 4)\% & (11, 25)\% & (6, 9)\% & (60, 60)\% \\
	\end{tabular}
\caption{The median percent of time participants spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage independent for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

%\begin{table}[t]
%\centering
%	\begin{tabular}{c r r r r}
%	& First & Proxy & Bridge & Progress \\
%	\noalign{\hrule}
%	All & 5\% & 17\% & 6\% & 64\% \\
%	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
%	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
%	E2-NEW & 5\% & 4\% & 4\% & 80\% \\
%	E2-OLD & 4\% & 22\% & 4\% & 66\% \\
%	E3-NEW & 6\% & 7\% & 4\% & 70\% \\
%	E3-OLD & 4\% & 25\% & 9\% & 60\% \\
%	\end{tabular}
%\caption{The overall percent of time all participants spent on each screen, computed by
%dividing the aggregate number of time on a screen by the aggregate time on all screens.} 
%\label{table:overall_time}
%\end{table}

>>>>

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Active-time configuration.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

@@

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	All & 7\% & 5\% & 4\% & 58\% \\
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 5\% & 5\% & 5\% & 76\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 3\% & 3\% & 5\% & 73\% \\
	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
	\end{tabular}
\caption{The median percent of time participants spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage independent for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

%\begin{table}[t]
%\centering
%	\begin{tabular}{c r r r r}
%	& First & Proxy & Bridge & Progress \\
%	\noalign{\hrule}
%	All & 5\% & 16\% & 6\% & 60\% \\
%	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
%	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
%	E2-NEW & 4\% & 3\% & 3\% & 58\% \\
%	E2-OLD & 4\% & 22\% & 4\% & 65\% \\
%	E3-NEW & 5\% & 6\% & 4\% & 64% \\
%	E3-OLD & 4\% & 25\% & 8\% & 56\% \\
%	\end{tabular}
%\caption{The overall percent of time all participants spent on each screen, computed by
%dividing the aggregate number of time on a screen by the aggregate time on all screens.} 
%\label{table:overall_time}
%\end{table}
